Opportunities for improvement in the care of adult trauma patients arriving

### 2025-02-16 manuscript.Rmd
ändrade plats för mallen

# Discussion
The purpose of this study was to assess the association between OFI and adult trauma patients arriving in shock, focusing on the types of OFI and severity of shock.

@@

```{=html}
<!--

-->
```
# Conclusion

<!-- Give a short conclusion, corresponding to the aim -->

>>>>

# Discussion
```{=html}
<!--

-->
```
The purpose of this study was to assess the association between OFI and adult trauma patients arriving in shock, focusing on the types of OFI and severity of shock.

@@

# Conclusion
<!-- Give a short conclusion, corresponding to the aim -->
